[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)

### 2020-03-09 analysis/paper.Rmd
Changes output to pdf so recreated tables can render properly

---
title: "[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)"
author: "Lauren Heintz, Tara Wilson, Ben Mathieu, Will Wright"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: bookdown::word_document2
bibliography: bibliography.bibtex
link-citations: yes

@@

```{r, table1-replication, fig.cap="Replication of Table 1", echo=FALSE}
knitr::include_graphics("table_1.png")
```

@@

The steps taken to reproduce this table are identical to those in the original publication aside from a new input dataset and the use of a combination of the kableExtra and xtable R packages to produce the output compared with xtable alone used in the original publication.

@@

```{r, table2-replication, fig.cap="Replication of Table 2", echo=FALSE}
knitr::include_graphics("table_2.png")
```

>>>>

---
title: "[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)"
author: "Lauren Heintz, Tara Wilson, Ben Mathieu, Will Wright"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
bibliography: bibliography.bibtex
link-citations: yes

@@

@@

The steps taken to reproduce this table are nearly identical to those in the original publication aside from a new input dataset.

@@
